\bf Auxiliary Model Approach to Strongly-Correlated Systems

### 2022-03-07 notes/notes.tex
added gen SIAM correlations

\begin{figure}[htpb]
\centering
\includegraphics[width=0.5\textwidth]{../figures/correlated_bath.png}
\caption{"Comparison of the usual Anderson
impurity model of a strongly interacting site coupled via $V$ to
an uncorrelated featureless and wide conduction-electron band
(left-hand side) and the Hubbard model situation (right-hand
side). In the latter case, an electron leaving a correlated site
moves within the strongly correlated and narrow band of the
central peak. In this situation there is a kink at the effective
Kondo energy scale which is smaller than the width of the
narrow band." Image and caption source in footnote.}
\end{figure}
\section{Introduction}
This is an attempt to obtain various quantities like Greens functions, self-energies, spectral functions and (if possible) energies and wavefunctions of the Hubbard model, using a cluster-bath approach. The cluster-bath system is taken to be a single-impurity Anderson model with a correlated bath. The correlation will be brought about in two ways: a self-energy $\Sigma(k,\omega)$ of the bath, and a double occupancy repulsion cost $U_b$. The Hubbard and the correlated single-impurity Anderson models are defined using the Hamiltonians
\begin{align}
H_\text{hubb} &= -t^H\sum_{\sigma,\left<i,j \right>}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right) + U^H\sum_i \hat n_{i \uparrow} \hat n_{i \downarrow} - \mu^H \sum_{i\sigma}\hat n_{i\sigma}\\
H_\text{siam} &= \sum_{k\sigma}\left[\epsilon_k + \Sigma(k,\omega)\right]\hat n_{k\sigma} + \epsilon_d^A \sum_\sigma\hat n_{d\sigma} + U^A \hat n_{d \uparrow} \hat n_{d \downarrow} + U_b \sum_{kk^\prime}\hat n_k \hat n_{k^\prime} -t^A\sum_{k\sigma}\left(c^\dagger_{d\sigma}c_{k\sigma} + \text{h.c.}\right) \label{clus_bath_siam}
\end{align}
Broadly speaking, the method involves first solving the SIAM using a unitary renormalisation group approach, to get the low energy effective theory, and then combining the low energy Hamiltonians in a symmetrized fashion to get the Hamiltonian for the Hubbard model lattice. It is reminescent of dynamical mean-field theory (DMFT) - both involve an impurity-solver that solves an auxiliary system. The difference, however, lies in the following points:
\begin{itemize}
	\item While DMFT primarily works with Greens functions and self-energies, this method involves Hamiltonians. The impurity-solver in DMFT provides an impurity Greens function (which is then equated with the local Greens function of the bath), while the impurity-solver in this method actually provides a low energy Hamiltonian.
	\item The final step of DMFT is the self-consistency equation, where the impurity and bath-local quantities are set equal. This ensures all sites, along with the impurity site, have the same self-energy, something which is required on grounds of  translational invariance. The present method, however, brings about the translational invariance in a different way. It symmetrizes the Hamiltonians itself, such that all quantites then derived from the Hamiltonian are then guaranteed to have the symmetry.
\end{itemize}
The meaning of each of these statements will become clearer when we describe the method in more detail.

\section{Philosophy of the method}
The method is closely tied to the auxiliary system approach described in [CITE MARTIN]. We can view the full Hamiltonian as a sum of two component Hamiltonians \(H_1, H_2\) connected via the interaction term \(H_{12}\).
\begin{equation}\begin{aligned}
	H = \begin{pmatrix} H_1 && H_{12} \\ H_{12}^* && H_2 \end{pmatrix} = H_1 \ket{1}\bra{1} + H_2\ket{2}\bra{2} + H_{12}\ket{1}\bra{2} + H_{12}^*\ket{2}\bra{1}
\end{aligned}\end{equation}
where \(\ket{1(2)}\) actually represents a sum over all basis kets of the subsystem 1(2). As an example, we can split the the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice as follows:
\begin{equation}\begin{aligned}
	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_1} \\
		      &+ \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_2}\\
		      & -\underbrace{t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)}_{H_{12} + H_{12}^*}\\
\end{aligned}\end{equation}
The Greens function of the full Hamiltonian can also be split in a similar fashion:
\begin{equation}\begin{aligned}
	G(\omega) = \begin{pmatrix} G_1 && G_{12} \\ G_{12}^* && G_2 \end{pmatrix} 
\end{aligned}\end{equation}
The subsystem 1 is usually taken to be the "smaller system", and consequently, subsystem 2 represents the "bath".
The smaller system is typically chosen such that its eigenstates are known exactly.
Progress is then made by choosing a simpler version of the bath \(H_2\) and a simpler form also for its coupling \(H_{12}\) with the smaller system.
This combination of the smaller system and the simpler bath is then called the \textit{auxiliary system}.
A typical auxiliary system for the Hubbard model would be the SIAM, where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{12}\).
Such a construction is shown in fig.~\ref{cluster-bath}.
\begin{figure}[htpb!]
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/cluster-bath.png}
	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$. \textit{Right}: Extraction of the auxiliary (cluster+bath) system from the full lattice. The central site on left becomes the impurity site (red) on the right (with an onsite repulsion $\epsilon_d$), while the rest of the $N-1$ sites on the left form a conduction bath (green circles) (with dispersion $\epsilon_k$ and correlation modelled by the self-energy $\Sigma_k(\omega)$) that hybridizes with the impurity through the coupling $V$.}
	\label{cluster-bath}
\end{figure}
\textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model. To allow computing quantities, one would need to make the bath (which is a much larger system) simpler than the cluster (which is a single site). This distinction breaks the translational symmetry of the Hubbard model. For eg., if one chooses eq.~\ref{clus_bath_siam} as the auxiliary system, then the fact that the impurity has an onsite correlation while the bath only has a global capacitative cost $(\sim U_b N^2)$ means we have broken the symmetry between the cluster and the bath.}

@@

In a similar manner, we checked the variation of the spin and charge probabilities, \(c_s\) and \(c_c\), in the ground state, with increasing bandwith. The result is shown in fig.~\ref{c_vs_D}.
	\includegraphics[width=0.45\textwidth]{../figures/coeffs_vs_D_largeV.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/coeffs_vs_D_smallV.pdf}
	\caption{Variation of spin and charge fractions, \(c_s\) and \(c_c\), of the ground state, as a function of bare bandwidth \(D_0\). Left and right panels show the cases of \(J_0 < V_0\) and \(J_0 > V_0\) respectively.}
	\label{c_vs_D}
For both \(V_0 < J_0\) and \(V_0 > J_0\), we see that the spin contribution increases towards unity while the charge contribution vanishes. This indicates that at large bandwidth, the ground state becomes purely a spin singlet, formed purely by singly-occupied impurity states.
	\label{gstate_kondo}
	\lim_{D_0 \to \infty} \ket{\Psi}_1 = \frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) 
\section{Spectral function of the single-impurity Anderson model}
To get a better look at what we are getting into and what we should expect going forward, we first calculate the spectral function of the smaller single-impurity Anderson model that is obtained as the low-energy Hamiltonian of an URG analysis of the full SIAM. This ow energy effective Hamiltonian is
	\epsilon_d \hat n_d + U\hat n_{d \uparrow} \hat n_{d \downarrow} + v \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + \sum_{k \in \left[-\Lambda^*, \Lambda^*\right], \sigma}\epsilon_k \hat n_{k\sigma}
All the impurity couplings are fixed point values, and the momentum states of the bath now run over a reduced bandwidth. The subscript \(d\) indicates that the operator is that of the impurity, while the subscript \(0\) indicates it is of the zeroth site of the bath: \(c_0 = \frac{1}{\sqrt N}\sum_k c_k\). The spectral function of the SIAM is already known from other methods like the numerical renormalization group. For small values of \(U\), the spectral function consists of just the central quasiparticle excitation peak. At larger values of \(U\), we see the emergence of the two Hubbard side bands while the spectral weight at the centre decreases. We also calculated the spectral function of the low energy theory sing exact diagonalization. The plots are shown in fig.~\ref{siam_spec_func}.
	\includegraphics[width=\textwidth]{../figures/siam_specfunc_all.pdf}
	\caption{Spectral function of the effective SIAM Hamiltonian for various values of \(\frac{U}{\Delta}\). \(\Delta\) is defined by the height of the central peak in the non-interacting model \(U=0\). The inset shows a zoom-in of the final spectral function \(\left( \frac{U}{\Delta} = 19.71 \right)\) near \(\omega = 0\).}
	\label{siam_spec_func}
Because we kept only a discrete bath of 4 momentum states, \textit{we had to artificially enforce the constancy of the height of the central peak, using \cite{langreth1966}.} To convert the discrete sum of delta functions into a continuous spectrum, we broadened them using a Gaussian. Following \cite{bullaNRGreview}, we replace the delta-functions at \(\pm x_n \equiv \pm(E_n - E_0)\) by normalised Gaussian functions
	\delta(\omega \pm x_n) \to \frac{1}{\eta_n\sqrt \pi}e^{-\left(\frac{\omega \pm x_n}{\eta_n}\right)^2}
The parameter \(\eta_n\) determines the height and width of the Gaussian, and is chosen such that the higher energy poles are broader than the lower energy ones.
	\eta_n = 2\Delta + \frac{1}{2}|x_n| 
where \(\Delta = \frac{V^2}{t}\) is the relevant energy scale of the non-interacting problem and \(t\) is the tight-binding hopping parameter of the conduction bath.
The central peak (or equivalently, the central pole in the impurity Greens function) does not vanish even for exhorbitantly large values of \(\frac{U}{\Delta}\), implying that there is no stable local moment phase in the SIAM (a local moment phase would involve a gap at zero frequency in the impurity spectral function). Formally, the local moment phase will be stable only at \(U \to \infty\) or \(v^* = 0\).
We also checked how the width of the central peak varies with increasing \(U\). The behaviour is shown in fig.~\ref{fwhm}. The width was also fitted against a function, as shown in the plot.
	\includegraphics[width=0.55\textwidth]{../figures/width_vs_U_simple_fit.pdf}
	% \includegraphics[width=0.49\textwidth]{./width_vs_U_simple_fit_log.pdf}
	\caption{The decay of the full width at half maximum (FWHM) of the central peak, with increasing \(\frac{U}{\Delta}\). The behaviour satisfies a function of the form shown in the legend.}
	\label{fwhm}

@@

>>>>

\begin{figure}[htpb]
\centering
\includegraphics[width=0.5\textwidth]{../figures/correlated_bath.png}
\caption{"Comparison of the usual Anderson
impurity model of a strongly interacting site coupled via $V$ to
an uncorrelated featureless and wide conduction-electron band
(left-hand side) and the Hubbard model situation (right-hand
side). In the latter case, an electron leaving a correlated site
moves within the strongly correlated and narrow band of the
central peak. In this situation there is a kink at the effective
Kondo energy scale which is smaller than the width of the
narrow band." Image and caption source in footnote.}
\end{figure}

This is an attempt to obtain various quantities like Greens functions, self-energies, spectral functions and (if possible) energies and wavefunctions of the Hubbard model, using a cluster-bath approach. The cluster-bath system is taken to be a single-impurity Anderson model with a correlated bath. The correlation will be brought about in two ways: a self-energy $\Sigma(k,\omega)$ of the bath, and a double occupancy repulsion cost $U_b$. The Hubbard and the correlated single-impurity Anderson models are defined using the Hamiltonians
\begin{align}
H_\text{hubb} &= -t^H\sum_{\sigma,\left<i,j \right>}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right) + U^H\sum_i \hat n_{i \uparrow} \hat n_{i \downarrow} - \mu^H \sum_{i\sigma}\hat n_{i\sigma}\\
H_\text{siam} &= \sum_{k\sigma}\left[\epsilon_k + \Sigma(k,\omega)\right]\hat n_{k\sigma} + \epsilon_d^A \sum_\sigma\hat n_{d\sigma} + U^A \hat n_{d \uparrow} \hat n_{d \downarrow} + U_b \sum_{kk^\prime}\hat n_k \hat n_{k^\prime} -t^A\sum_{k\sigma}\left(c^\dagger_{d\sigma}c_{k\sigma} + \text{h.c.}\right) \label{clus_bath_siam}
\end{align}
Broadly speaking, the method involves first solving the SIAM using a unitary renormalisation group approach, to get the low energy effective theory, and then combining the low energy Hamiltonians in a symmetrized fashion to get the Hamiltonian for the Hubbard model lattice. It is reminescent of dynamical mean-field theory (DMFT) - both involve an impurity-solver that solves an auxiliary system. The difference, however, lies in the following points:
\begin{itemize}
	\item While DMFT primarily works with Greens functions and self-energies, this method involves Hamiltonians. The impurity-solver in DMFT provides an impurity Greens function (which is then equated with the local Greens function of the bath), while the impurity-solver in this method actually provides a low energy Hamiltonian.
	\item The final step of DMFT is the self-consistency equation, where the impurity and bath-local quantities are set equal. This ensures all sites, along with the impurity site, have the same self-energy, something which is required on grounds of  translational invariance. The present method, however, brings about the translational invariance in a different way. It symmetrizes the Hamiltonians itself, such that all quantites then derived from the Hamiltonian are then guaranteed to have the symmetry.
\end{itemize}
The meaning of each of these statements will become clearer when we describe the method in more detail.

\section{Philosophy of the auxiliary model method}
The method is closely tied to the auxiliary system approach described in [CITE MARTIN]. We can view the full Hamiltonian as a sum of two component Hamiltonians \(H_1, H_2\) connected via the interaction term \(H_{12}\).
\begin{equation}\begin{aligned}
	H = \begin{pmatrix} H_1 && H_{12} \\ H_{12}^* && H_2 \end{pmatrix} = H_1 \ket{1}\bra{1} + H_2\ket{2}\bra{2} + H_{12}\ket{1}\bra{2} + H_{12}^*\ket{2}\bra{1}
\end{aligned}\end{equation}
where \(\ket{1(2)}\) actually represents a sum over all basis kets of the subsystem 1(2). As an example, we can split the the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice as follows:
\begin{equation}\begin{aligned}
	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_1} \\
		      &+ \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_2}\\
		      & -\underbrace{t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)}_{H_{12} + H_{12}^*}\\
\end{aligned}\end{equation}
The Greens function of the full Hamiltonian can also be split in a similar fashion:
\begin{equation}\begin{aligned}
	G(\omega) = \begin{pmatrix} G_1 && G_{12} \\ G_{12}^* && G_2 \end{pmatrix} 
\end{aligned}\end{equation}
The subsystem 1 is usually taken to be the "smaller system", and consequently, subsystem 2 represents the "bath".
The smaller system is typically chosen such that its eigenstates are known exactly.
Progress is then made by choosing a simpler version of the bath \(H_2\) and a simpler form also for its coupling \(H_{12}\) with the smaller system.
This combination of the smaller system and the simpler bath is then called the \textit{auxiliary system}.
A typical auxiliary system for the Hubbard model would be the SIAM, where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{12}\).
Such a construction is shown in fig.~\ref{cluster-bath}.
\begin{figure}[htpb!]
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/cluster-bath.png}
	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$. \textit{Right}: Extraction of the auxiliary (cluster+bath) system from the full lattice. The central site on left becomes the impurity site (red) on the right (with an onsite repulsion $\epsilon_d$), while the rest of the $N-1$ sites on the left form a conduction bath (green circles) (with dispersion $\epsilon_k$ and correlation modelled by the self-energy $\Sigma_k(\omega)$) that hybridizes with the impurity through the coupling $V$.}
	\label{cluster-bath}
\end{figure}
\textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model. To allow computing quantities, one would need to make the bath (which is a much larger system) simpler than the cluster (which is a single site). This distinction breaks the translational symmetry of the Hubbard model. For eg., if one chooses eq.~\ref{clus_bath_siam} as the auxiliary system, then the fact that the impurity has an onsite correlation while the bath only has a global capacitative cost $(\sim U_b N^2)$ means we have broken the symmetry between the cluster and the bath.}

@@

In a similar manner, we checked the variation of the spin and charge probabilities, \(c_s\) and \(c_c\), in the ground state, with increasing bandwith. The result is shown in fig.~\ref{c_vs_D}.
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.45\textwidth]{../figures/coeffs_vs_D_largeV.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/coeffs_vs_D_smallV.pdf}
	\caption{Variation of spin and charge fractions, \(c_s\) and \(c_c\), of the ground state, as a function of bare bandwidth \(D_0\). Left and right panels show the cases of \(J_0 < V_0\) and \(J_0 > V_0\) respectively.}
	\label{c_vs_D}
\end{figure}
For both \(V_0 < J_0\) and \(V_0 > J_0\), we see that the spin contribution increases towards unity while the charge contribution vanishes. This indicates that at large bandwidth, the ground state becomes purely a spin singlet, formed purely by singly-occupied impurity states.
\begin{equation}\begin{aligned}
	\label{gstate_kondo}
	\lim_{D_0 \to \infty} \ket{\Psi}_1 = \frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) 
\end{aligned}\end{equation}

@@

\section{Destruction of the Abrikosov-Suhl resonance: transition from strong-coupling to local moment}

We will now tune the parameters of the fixed point Hamiltonian and study the variation of quantities related to the effective Hamiltonian like the local FL strength \(\mathcal{F}\), the gap in the spectrum of the zeroth Hamiltonian \(H_0^*\) and the value of the small parameter \(t^2/\delta E\), as well as various measures of entanglement like entanglement entropy, mutual information and spin-spin correlations between various sets of members of the real-space impurity+lattice construction. We will trace a specific path through the space of values of fixed point couplings: we will start from the strong-coupling regime \(U \ll J,V\) and go towards the local moment regime \(U \gg J,V\). The context of this study is that the technique of dynamical mean-field theory (DMFT) obtains a metal-insulator transition in the 2D Hubbard model by studying the Anderson impurity model as the auxiliary system for the Hubbard; there, the local moment regime of the impurity corresponds to the insulator in the bulk. Our goal here is to study what precisely happens in the effective Hamiltonian in the journey from the metal to the insulator, and draw a concrete connection between this modification of the effective Hamiltonian, and the simultaneous change of the impurity spectral function in fig.~\ref{spec_func}. This is done with the knowledge that the local moment phase of the generalised SIAM is never RG-stable.

\subsection*{Perturbation theory parameters}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
\end{center}
The vanishing of the gap and the growth of the small parameter indicates the breakdown of perturbation theory around the singlet; this simply shows that there is a degeneracy in the local moment regime, and the effective Hamiltonian will have to be obtained using degenerate perturbation theory. The presence of degeneracy also suggests that the effective Hamiltonian will be of the non-Fermi liquid type.

\subsection*{\(k-\)space correlations within the Kondo cloud}
\begin{center}
	\includegraphics[width=0.24\textwidth]{../figures/corr-k-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
	\includegraphics[width=0.24\textwidth]{../figures/mi-dk-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
	\includegraphics[width=0.24\textwidth]{../figures/corr-k-diag-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
	\includegraphics[width=0.24\textwidth]{../figures/corr-k-od-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
\end{center}
The vanishing of the Kondo cloud at large \(U/J\) is clear indication of the destruction of the Kondo cloud and the breakdown of screening. Non-zero mutual information indicates an (impurity-mediated) interaction between the \(k-\)states of the conduction bath; seen differently, it is this interaction that is responsively for the screening of the impurity. The disappearance of the mutual information is indicative of the disappearance of this interaction.

\subsection*{Mutual information between various real space members}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
\end{center}
The impurity-zeroth site mutual information \(I(d:0)\) remains unchanged at the maximum for an appreciable range of values, and this shows the stability of the singlet. Meanwhile, the mutual information between the zeroth site and the site nearest to it (\(I(0:1)\)) grows, because when the singlet weakens, the zeroth site is able to entangle more with the other sites. It finally saturates to its maximum value, which is the value produced as result of the tight-binding hopping. The mutual information between the impurity and sites beyond the zeroth site (\(I(d:1)\)) show a non-monotonic behaviour; it first increases as the entanglement that was initially restricted to just the impurity and the zeroth sites begins "seeping" into the other sites as well. Beyond a critical value of \(U/J\), \(I(d:1)\) starts dropping, because the entanglement has now mostly shifted out of the zero mode and into the conduction bath.

\subsection*{Impurity entanglement entropy and spin-spin correlations}

\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}

	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
\end{center}

The von-Neumann entanglement entropy \(S(d)\) of the impurity shows pretty straightforward behaviour. It is maximum for \(U \ll J\) because it is in a singlet configuration. For \(U \gg J\), the singlet weakens and the impurity begins to decouple from the bath, leading to a reduction in \(S(d)\). At sufficiently low values of \(J/U\), the impurity decouples from the zeroth site and the total system can be factorised into a local moment in product with a tight-binding chain, so that the impurity site will now have zero entanglement entropy.

\subsection*{Behaviour of real-space correlations}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}

	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
\end{center}

\subsection*{Behaviour of real-space correlations as function of distance}
\begin{center}
	\includegraphics[width=0.35\textwidth]{../figures/corr-di-min-t=1.000,J=1_over_U,V=J,N=6,U=0.010,100.000,100.pdf}
	\includegraphics[width=0.35\textwidth]{../figures/corr-di-max-t=1.000,J=1_over_U,V=J,N=6,U=0.010,100.000,100.pdf}

	\includegraphics[width=0.45\textwidth]{../figures/corr-all-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
	\includegraphics[width=0.45\textwidth]{../figures/I-all-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
\end{center}

\subsection*{Behaviour of \(A(\omega)\)}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=0.100.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=9.000.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=16.000.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=20.250.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=36.000.pdf}
\end{center}
